SAT Solving for Vesicle Traffic Systems in Cells

### 2017-07-20 paper/intro_MTedit.tex
footnote

% \todo{REQUIRE A REWRITE FLOW PROBS}
In this paper, we have developed a novel SAT encoding for
searching VTSs that satisfy the useful properties.
%
We have improved the encoding of some of the conditions for VTSs.
%
Especially, we have recursively defined the reachability condition
such that that we avoid the inefficient enumeration.
%
% We have also encoded $k$-connectivity in a similar fashion and avoided
% a blowup in the formula size.
%
% Furthermore, our encoding supports several variations of the properties.
%
We have implemented the encoding using Z3~\cite{z3} python API and
searched for VTS satisfying various properties upto size 14-18 nodes
as compare earlier tool that could only search graph upto
size~6\footnote{The experiments in~\cite{shukla} scale upto 8.
However, our experiments only scale upto 6, because
we are using less powerful machine.} nodes.
%
Our tool is useful to cell biologists since VTSs of real cells have
approximately 10 compartments.

>>>>

% \todo{REQUIRE A REWRITE FLOW PROBS}
In this paper, we have developed a novel SAT encoding for
searching VTSs that satisfy the useful properties.
%
We have improved the encoding of some of the conditions for VTSs.
%
Especially, we have recursively defined the reachability condition
such that that we avoid the inefficient enumeration.
%
% We have also encoded $k$-connectivity in a similar fashion and avoided
% a blowup in the formula size.
%
% Furthermore, our encoding supports several variations of the properties.
%
We have implemented the encoding using Z3~\cite{z3} python API and
searched for VTS satisfying various properties upto size 14-18 nodes
as compare earlier tool that could only search graph upto
size~6\footnote{The original experiments in~\cite{shukla} scaled upto 8.
However, our current experiments only scale upto 6, because
we are using less powerful machine.} nodes.
%
Our tool is useful to cell biologists since VTSs of real cells have
approximately 10 compartments.
